---
title: "hw8"
author: "Katie Rhodes"
format: pdf
---
```{r}
library(tidyverse)
library(forcats)
library(lubridate)
library(readr)
library(stringr)
library(rvest)
library(dplyr) 
library(nycflights13)

```
1) 
Use formula Sn = (n)(n+1)(2n+1)/6
```{r}

compute_sumsq <- function(n) {
  n * (n+1) * (2*n+1)/6
}
compute_sumsq(n=15)
compute_sumsq(n=27)
```

2) 

```{r}
url <- "https://www.boxofficemojo.com/year/2024/"
movie_table <- read_html(url) |>
  html_elements("table") |>
  html_table() |>
  pluck(1) |>
  mutate(
    Gross = parse_number(Gross),
    Theaters = parse_number(Theaters),
    `Total Gross` = parse_number(`Total Gross`),
    `Release Date` = lubridate::mdy(str_glue("{`Release Date`} 2024"))
  ) |>
  select(-Genre, -Budget, -`Running Time`, -Estimated)
```
a) Write a function called scrape_bomojo() that scrapes information about the domestic box office performance in a specified year. This function should do the following:

have one input: the URL of the webpage
return a data frame
rename variables scraped, using snake_case (Hint: consider the janitor::clean_names() function)
```{r}
scrape_bomojo <- function(url){
  page <- read_html(url) 
  movie_table <- page |>
    html_elements("table") |>
    html_table() |>
    pluck(1) |>
    janitor::clean_names() |>
    mutate(
      gross = parse_number(gross), 
      total_gross = parse_number(total_gross),
      theaters = parse_number(theaters), 
      month = word(release_date, 1), 
      day = parse_number(release_date))

}

print(scrape_bomojo("https://www.boxofficemojo.com/year/2024/"))
```
b) 
```{r}
scrape_bomojo2 <- function(year) {
  url <- str_c("https://www.boxofficemojo.com/", year, "/")
  page <- read_html(url) 
  movie_table <- page |>
    html_elements("table") |>
    html_table() |>
    pluck(1) |>
    janitor::clean_names() |>
    mutate(
      gross = parse_number(gross), 
      total_gross = parse_number(total_gross),
      theaters = parse_number(theaters), 
      month = word(release_date, 1), 
      day = parse_number(release_date))

}
```

3) Using the datasets from nycflights13, write a function that:

a) Finds all flights that were cancelled (i.e. is.na(arr_time)) or delayed by more than an hour.
```{r}
flights_severe <- function(flights) {
  flights |> 
    filter(is.na(arr_time))
}
severe_flights <- flights |> flights_severe()
```
b) Counts the number of cancelled flights and the number of flights delayed by more than an hour.
```{r}
summarize_b <- function(flights) {
  flights |>
    summarize(cancelled = sum(is.na(arr_time)), delayed_1hr = sum(arr_delay > 60, na.rm = TRUE))
}

b <- flights |> 
  group_by(dest) |> 
  summarize_b()
```
c) Finds all flights that were cancelled or delayed by more than a user supplied number of hours:
```{r}
filter_severe <- function(flights, hours) {
  min_hour <- hours * 60
  flights |>
    filter(is.na(arr_time) | arr_delay > min_hour)
}
c<- flights |> filter_severe(hours = 2)
```
d) Summarizes the weather to compute the minimum, mean, and maximum, of a user supplied variable:
```{r}
summarize_variable_d <- function(flights, var) {
 flights |> 
    summarize(
      min_val  = min(flights[[var]], na.rm = TRUE),
      mean_val = mean(flights[[var]], na.rm = TRUE),
      max_val  = max(flights[[var]], na.rm = TRUE)
    )
}
```

e) Converts the user supplied variable that uses clock time (e.g., dep_time, arr_time, etc.) into a decimal time (i.e. hours + (minutes / 60)).
```{r}
standardize_time <- function(flights, time_var) {
flights[[time_var]] <- (flights[[time_var]] %/% 100) + ((flights[[time_var]] %% 100) / 60)

}
e <- flights |> standardize_time("sched_dep_time")
```

4) 
```{r}
commute <- read.csv("http://aloy.rbind.io/data/CommuteAtlanta.csv")
```

The Time column contains the commute times of these 500 individuals.

Your task is to run a one-sample bootstrap and calculate a 95% percentile confidence interval for the average commute time in Atlanta, GA. To do this, write a for loop that does the following:

Use the dplyr::slice_sample() function to select a random sample of rows from the data frame, with replacement. Be sure that your data set for the random sample has the same number of rows as the original data set. In addition, don’t hesitate to look at the help file for dplyr::slice_sample() to see how to specify the sample size and ensure that you are sampling with replacement.
From this resampled data set, calculate the sample mean commute time and store the result.
Repeat steps 1-2 1,000 times.
Once you have your 1,000 sample means calculated, calculate the 0.025 and 0.975 quantiles of this vector using the quantile() function. This is a 95% percentile confidence interval.

```{r}
n <- nrow(commute) 
boot_means <- numeric(1000) 
for (i in 1:1000) {
  sample <- commute |>
    slice_sample(n =n, replace = TRUE)
    boot_means[i] <- mean(sample$Time)
}
quantile(boot_means, 0.025)
quantile(boot_means, 0.975)
```

5) A random walk proceeds as follows:
A walker chooses a starting point on a line and then decides to take one step right or left at random, dependent on the toss of a fair coin (e.g., 50% chance of heads, 50% chance of tails).
If the coin is HEADS, they move right, if it comes up TAILS then the move is to the left.
The second step proceeds in the same manner, and so on for each subsequent step.

Your task is to use a for loop and if-else statements to implement a random walk and plot the first 100 steps the walker takes. To do this, here are a few hints:

Start the walker at (x = 0, y = 0), and use x to track the number of steps and y to track whether they are going to the left (-1) or right (+1).

You can use sample(c("heads", "tails"), size = 1) to flip a fair coin a single time.

The plot you construct should look similar to the plot below, though of course it will be different since these are random processes!
```{r}
n_steps <- 100
x <- 0:n_steps
y <- numeric(n_steps + 1) 
y[1] <- 0 

for (i in 2:(n_steps + 1)) {
  coin <- sample(c("heads", "tails"), size = 1)
  if (coin == "heads") {
    step <- 1 }
    else {
      step <- -1 }
    y[i] <- y[i-1] + step
    
}
walk_random <- data.frame(Step = x, Position = y) 
ggplot(walk_random, aes(x = Step, y = Position)) + geom_point() + geom_line()
```

